---
title: "R Final Project"
format: html
editor: visual
---

# Covid Testing

This is an analysis of a cross-sectional study of the de-identified data on COVID-19 testing, and provides a snapshot of the first 100 days of testing during the year 2020 at the Children’s Hospital of Pennsylvania (aka CHOP).

## Initialising the libraries

This involves loading the installed packages to use the built-in functions in them

```{r}
#| echo: false
#| warning: false
#| message: false
library(tidyverse)
library(gtsummary)
library(here)
library(dplyr)
here::here ("Final project", "covid_testing.rda")

```

## Descriptive statistics table

```{r}
#| echo: false
#| label: table-one
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
#| error: false

load(file = 'covid_testing.rda')

Description_table <- tbl_summary(
	covid_testing,
	by = gender,
	include = c(age, pan_day, result, payor_group, demo_group, patient_class),
    label = list(
		pan_day ~ "Pandemic day",
		payor_group ~ "Payor",
		demo_group ~ "Demographic",
		patient_class ~ "Patient class",
		age ~ "Age",
		result ~ "Result"
	),
	missing_text = "Missing")

Description_table


```
@table-one contains a descriptive statistics table.

```{r}
#| echo: false
c2 <- covid_testing %>% mutate(Demographic = factor(demo_group, labels = c("client","patient", "other adult", "misc adult", "unidentified")),
			  Result = factor(result, labels = c("positive", "negative", "invalid")))
```

## Univariate regression analysis

```{r}
#| echo: false
#| label: table-two
#| tbl-cap: "Regression Analysis"
#| output-location: slide

Regression_table <- tbl_uvregression(
       c2,
	y = age,
	include = c(Demographic, gender, result),
	method = lm)

Regression_table

```

@table-two contains a regression table 

## Histogram for pandemic day

```{r}
#| echo: false
#| label: Figure
#| fig-cap: "Histogram of covid testing day from pandemic"
#| fig-cap-location: top

hist(covid_testing$pan_day)

```
@Figure contains a histogram 

## Functions

```{r}
#| echo: false
#| output-location: slide

#mean

mn <- function(x){
	m <- mean(x)
	return (m)
}
mn(c2$pan_day)

# Standard deviation after handling missing values

std_dev <- function(x){
		clean_data <- x[!is.na(x)]
		sd_value <- sd(clean_data)
		return (sd_value)}

std_dev(c2$pan_day)

```

```{r}
#|echo: false

gtsummary::inline_text(Description_table, variable = "patient_class", level = "admit after surgery-ip", column = "female")
```
A greater proportion of female (`r inline_text(Description_table, variable = "result", level="positive", column = "female")`) than male(`r inline_text(Description_table, variable = "result", level="positive", column = "male")`) participants were affected by COVID-19.

```{r}

```
